Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-17 paper/main.tex
Event description

\documentclass[english]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{babel}
\usepackage{comment}
\usepackage{svg}
\usepackage{caption, booktabs}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{fancyhdr}
% \usepackage[disable]{todonotes}
\usepackage{todonotes}
\usepackage{units}
\usepackage[left=2cm,right=4cm,top=2cm,bottom=2cm]{geometry}
\usepackage[
colorlinks=true,
	citecolor=black,
  urlcolor=black,
	linkcolor=black
]{hyperref}
\newcommand{\scidatalogo}{\includegraphics[height=36pt]{SciData_logo.jpg}}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\setlength{\headheight}{40pt}
\lhead{\textsc{\scidatalogo}}
\usepackage{natbib}

@@

% traditionally
Traditionally, researchers design stimuli that presumably would trigger the
perceptual process of interest while also controlling confounding variables
(e.g. color, luminance).
% our approach: annotation and regressors
Naturalistic stimuli mimic how we experience the world more closely but have the
drawback that they are usually fix and that their temporal structure is unknown.
% annotation ftw
Hence, we annotated the temporal structure of various stimulus features that
later served as basis for modeling hemodynamic responses.

% AV anno
For the analysis of the movie stimulus, we took advantage of a previously published
annotation of 869 movie cuts and the depicted location after each cut
\citep{haeusler2016cutanno}.
% rationale to use that annotation rationale behind using movie cuts
Our rationale was that cuts are ``spatially relevant'' events that re-orient the
viewer within the environment of the movie by either switching to another
setting or switching the perspective within the same setting.
% AV regressors/events
Each cut was put into one of the following five categories (see Table
\ref{tab:av-events}):
%
1) a cut switching to a setting that was depicted for the first time
(\texttt{vse\_new}),
%
2) a cut switching to a setting that was already depicted earlier in the movie
(\texttt{vse\_old}),
%
3) a cut switching to another locale within a setting (\texttt{vlo\_ch}; e.g. a
cut from first to the second floor in Forrest's house),
%
4) a cut to another camera position within a setting or locale that was depicted
for the first time (\texttt{vpe\_new}), and
%
5) a cut to another camera position within a setting or locale that was already
depicted before (\texttt{vpe\_old}).

@@

vse\_new &  change of the camera position to a setting not depicted before & \aoVsenewAll & \aoVsenewI & \aoVsenewII & \aoVsenewIII & \aoVsenewIV & \aoVsenewV & \aoVsenewVI & \aoVsenewVII & \aoVsenewVIII
\tabularnewline vse\_old & change of the camera position to a recurring setting & \aoVseoldAll & \aoVseoldI & \aoVseoldII & \aoVseoldIII & \aoVseoldIV & \aoVseoldV & \aoVseoldVI & \aoVseoldVII & \aoVseoldVIII

@@

vlo\_ch & change of the camera position to another locale within the same setting & \aoVlochAll & \aoVlochI & \aoVlochII & \aoVlochIII & \aoVlochIV & 0 & \aoVlochV & \aoVlochVI & \aoVlochVII

@@

vpe\_new & change of the camera position within a locale not depicted before & \aoVpenewAll & \aoVpenewI & \aoVpenewII & \aoVpenewIII & \aoVpenewIV & \aoVpenewV & \aoVpenewVI & \aoVpenewVII & \aoVpenewVIII

@@

vpe\_old & change of the camera position within a recurring locale &

@@

vno\_cut & frames within a continuous movie shot & \avVnocutAll & \avVnocutI & \avVnocutII & 0 & \avVnocutIII & \avVnocutIV & \avVnocutV & \avVnocutVI & \avVnocutVII

@@

fg\_av\_ger\_lr & left-right luminance difference & \avFgavgerlrAll & \avFgavgerlrI & \avFgavgerlrII & \avFgavgerlrIII & \avFgavgerlrIV & \avFgavgerlrV & \avFgavgerlrVI & \avFgavgerlrVII & \avFgavgerlrVIII

@@

fg\_av\_ger\_lrdiff & left-right volume difference & \avFgavgerlrdiffAll & \avFgavgerlrdiffI & \avFgavgerlrdiffII & \avFgavgerlrdiffIII & \avFgavgerlrdiffIV & \avFgavgerlrdiffV & \avFgavgerlrdiffVI & \avFgavgerlrdiffVII & \avFgavgerlrdiffVIII

@@

fg\_av\_ger\_ml & mean luminance & \avFgavgermlAll & \avFgavgermlI & \avFgavgermlII & \avFgavgermlIII & \avFgavgermlIV & \avFgavgermlV & \avFgavgermlVI & \avFgavgermlVII & \avFgavgermlVIII

@@

fg\_av\_ger\_pd & perceptual difference & \avFgavgerpdAll & \avFgavgerpdI & \avFgavgerpdII & \avFgavgerpdIII & \avFgavgerpdIV & \avFgavgerpdV & \avFgavgerpdVI & \avFgavgerpdVII & \avFgavgerpdVIII

@@

fg\_av\_ger\_rms & root mean square volume & \avFgavgerrmsAll & \avFgavgerrmsI & \avFgavgerrmsII & \avFgavgerrmsIII & \avFgavgerrmsIV & \avFgavgerrmsV & \avFgavgerrmsVI & \avFgavgerrmsVII & \avFgavgerrmsVIII

@@

fg\_av\_ger\_ud & upper-lower luminance difference & \avFgavgerudAll & \avFgavgerudI & \avFgavgerudII & \avFgavgerudIII & \avFgavgerudIV & \avFgavgerudV & \avFgavgerudVI & \avFgavgerudVII & \avFgavgerudVIII

>>>>

\documentclass[english]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{babel}
\usepackage{comment}
\usepackage{svg}
\usepackage{caption, booktabs}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{fancyhdr}
% \usepackage[disable]{todonotes}
\usepackage{todonotes}
\usepackage{units}
\usepackage[left=2cm,right=4cm,top=2cm,bottom=2cm]{geometry}
\usepackage[
colorlinks=true,
	citecolor=black,
  urlcolor=black,
	linkcolor=black
]{hyperref}
%\newcommand{\scidatalogo}{\includegraphics[height=36pt]{SciData_logo.jpg}}
\newcommand{\scidatalogo}{}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\setlength{\headheight}{40pt}
\lhead{\textsc{\scidatalogo}}
\usepackage{natbib}

@@

% traditionally
In contrast to stimuli designed to trigger a perceptual process of interest,
while controlling for confounding variables (e.g., color and luminance),
% our approach: annotation and regressors
naturalistic stimuli have an initially unknown temporal structure
of stimulus features of interest, as well as an equally unknown confound structure.
% annotation ftw
In order to evaluate the suitability of the stimulus for the targeted analyses,
and well as to inform the required hemodynamic models, we annotated the temporal
structure of a range of stimulus features.

% AV anno
For the analysis of the movie stimulus, we took advantage of a previously
published annotation of 869 movie cuts and the depicted location after each cut
\citep{haeusler2016cutanno}.
% rationale to use that annotation rationale behind using movie cuts
We conceptualized cuts as events with information on the depicted environment
that require viewers to re-orient themselves within the movie environment by
switching to a new perspective within the same setting, or to a position in an
entirely different setting.
% AV regressors/events
We assigned each cut to one of five categories (see Table
\ref{tab:av-events}):
%
1) a cut switching to a setting that was depicted for the first time
(\texttt{vse\_new}),
%
2) a cut switching to a setting that was already depicted earlier in the movie
(\texttt{vse\_old}),
%
3) a cut switching to another locale within a setting (\texttt{vlo\_ch}; e.g. a
cut from first to the second floor in Forrest's house),
%
4) a cut to another camera position within a setting or locale that was depicted
for the first time (\texttt{vpe\_new}), and
%
5) a cut to another camera position within a setting or locale that was already
depicted before (\texttt{vpe\_old}).

@@

\texttt{vse\_new} &  change of the camera position to a setting not depicted before & \aoVsenewAll & \aoVsenewI & \aoVsenewII & \aoVsenewIII & \aoVsenewIV & \aoVsenewV & \aoVsenewVI & \aoVsenewVII & \aoVsenewVIII

@@

\texttt{vse\_old} & change of the camera position to a recurring setting & \aoVseoldAll & \aoVseoldI & \aoVseoldII & \aoVseoldIII & \aoVseoldIV & \aoVseoldV & \aoVseoldVI & \aoVseoldVII & \aoVseoldVIII

@@

\texttt{vlo\_ch} & change of the camera position to another locale within the same setting & \aoVlochAll & \aoVlochI & \aoVlochII & \aoVlochIII & \aoVlochIV & 0 & \aoVlochV & \aoVlochVI & \aoVlochVII
\texttt{vpe\_new} & change of the camera position within a locale not depicted before & \aoVpenewAll & \aoVpenewI & \aoVpenewII & \aoVpenewIII & \aoVpenewIV & \aoVpenewV & \aoVpenewVI & \aoVpenewVII & \aoVpenewVIII

@@

\texttt{vpe\_old} & change of the camera position within a recurring locale &

@@

\texttt{vno\_cut} & frames within a continuous movie shot & \avVnocutAll & \avVnocutI & \avVnocutII & 0 & \avVnocutIII & \avVnocutIV & \avVnocutV & \avVnocutVI & \avVnocutVII

@@

\texttt{fg\_av\_ger\_lr} & left-right luminance difference & \avFgavgerlrAll & \avFgavgerlrI & \avFgavgerlrII & \avFgavgerlrIII & \avFgavgerlrIV & \avFgavgerlrV & \avFgavgerlrVI & \avFgavgerlrVII & \avFgavgerlrVIII

@@

\texttt{fg\_av\_ger\_lrdiff} & left-right volume difference & \avFgavgerlrdiffAll & \avFgavgerlrdiffI & \avFgavgerlrdiffII & \avFgavgerlrdiffIII & \avFgavgerlrdiffIV & \avFgavgerlrdiffV & \avFgavgerlrdiffVI & \avFgavgerlrdiffVII & \avFgavgerlrdiffVIII

@@

\texttt{fg\_av\_ger\_ml} & mean luminance & \avFgavgermlAll & \avFgavgermlI & \avFgavgermlII & \avFgavgermlIII & \avFgavgermlIV & \avFgavgermlV & \avFgavgermlVI & \avFgavgermlVII & \avFgavgermlVIII

@@

\texttt{fg\_av\_ger\_pd} & perceptual difference & \avFgavgerpdAll & \avFgavgerpdI & \avFgavgerpdII & \avFgavgerpdIII & \avFgavgerpdIV & \avFgavgerpdV & \avFgavgerpdVI & \avFgavgerpdVII & \avFgavgerpdVIII

@@

\texttt{fg\_av\_ger\_rms} & root mean square volume & \avFgavgerrmsAll & \avFgavgerrmsI & \avFgavgerrmsII & \avFgavgerrmsIII & \avFgavgerrmsIV & \avFgavgerrmsV & \avFgavgerrmsVI & \avFgavgerrmsVII & \avFgavgerrmsVIII

@@

\texttt{fg\_av\_ger\_ud} & upper-lower luminance difference & \avFgavgerudAll & \avFgavgerudI & \avFgavgerudII & \avFgavgerudIII & \avFgavgerudIV & \avFgavgerudV & \avFgavgerudVI & \avFgavgerudVII & \avFgavgerudVIII
